---
title: "Home Assignment"
author: "Dor Polovincik"
date: "4/4/2021"
output:
  rmarkdown::html_document:
    theme: lumen
---


```{r setup, include=FALSE}
library(dplyr)
library(ggplot2)
library(ggcharts)
library(reshape2)
library(purrr)
library(stringr)
library(reticulate)
source("data_wrangler.r")

customGreen = PARAMS$cols$customGreen
customGreen0 = PARAMS$cols$customGreen0
customRed = PARAMS$cols$customRed
```

# Question I

## KPIs Overview - General Population

```{r general_kpis,  fig.height=6, fig.width=7, message=FALSE, warning=FALSE, paged.print=TRUE, fig.align="center"}
general_kpi <- kpi_calculator(df)  %>%
  mutate_at(1:6, round, 3)

formattable(general_kpi, align = rep('c', 6))
```

---

## Segmentation

The grouping set is based on the following features permutation:

  * **billing_country_code**
* **shipping_country_code**
* **gateway**

I've also used the following features in order to show how Riskified can surpass current merchant solution:

  * **V4_our_age**
* **V1_link**

---

## Groups KPI Distributions {.tabset}

### Number of Orders

```{r segmentation,  fig.height=4, fig.width=7, message=FALSE, warning=FALSE, paged.print=TRUE, fig.align="center"}
required_features <- PARAMS$relevant_columns
df_aggregated <- kpi_calculator_multi(required_features) %>% 
  filter(total_orders > 40) %>%
  mutate(ar_z = (approval_rate - mean(approval_rate))/sd(approval_rate),
         cbr_z = (cb_rate - mean(cb_rate))/sd(cb_rate))

df_aggregated %>%
  ggplot(aes(x=total_orders, fill= PARAMS$cols$customGreen0)) +
  geom_density() + 
  theme_ggcharts() +   
  labs(title = 'Number of Orders by Group',
       subtitle = 'Distribution',
       fill = '',
       x = 'Number of Orders') + 
  theme(legend.position = 'none')
```

### Chargeback Rate

```{r cb_rate,  fig.height=4, fig.width=7, message=FALSE, warning=FALSE, paged.print=TRUE, fig.align="center"}
df_aggregated %>% 
  ggplot(aes(x=cb_rate, fill = PARAMS$cols$customGreen0)) +
  geom_density() + 
  theme_ggcharts() +   
  labs(title = 'Chargeback Rate by Group',
       subtitle = 'Distribution',
       fill = '',
       x = 'Chargeback Rate') + 
  theme(legend.position = 'none')
```

### Approval Rate

```{r approval_rate,  fig.height=4, fig.width=7, message=FALSE, warning=FALSE, paged.print=TRUE, fig.align="center"}
df_aggregated %>% 
  ggplot(aes(x=approval_rate, fill= PARAMS$cols$customGreen0)) +
  geom_density() + 
  theme_ggcharts() +   
  labs(title = 'Approval Rate by Group',
       subtitle = 'Distribution',
       fill = '',
       x = 'Approval Rate') + 
  theme(legend.position = 'none')
```

---

## Risky Segments {.tabset}

**Risky segments** will be defined as groups with the following attributes: 

  * Relatively **low Approval Rate**
* Relatively **high Chargeback Rate**

With the assumption of transaction that are mostly to be declined while having relatively high chargeback rate 
within specific groups, are very risky and Riskified can do a better job in terms of fraud detection and increasing approval rate.

### Table

```{r riski_segments_a,  fig.height=4, fig.width=9, message=FALSE, warning=FALSE, paged.print=TRUE, fig.align="center"}
df_risky <- df_aggregated  %>%
  filter(ar_z < -2, cbr_z > 2) %>%
  select(billing_country_code, shipping_country_code, gateway, total_orders,
         total_approved_volume, approval_rate, cb_rate) %>%
   mutate_at(4:7, round, 3) %>%
  arrange(desc(total_approved_volume), desc(total_orders))

formattable(df_risky, align =c("c","c","c","c","c", "c", "c"), 
            list(
              `total_orders`= color_tile(customGreen0, customGreen),
              `total_approved_volume`= color_tile(customGreen0, customGreen),
              `approval_rate`= color_tile(customGreen0, customGreen),
              `cb_rate`= color_bar(customRed)
            ))
```

### Chart

```{r riski_segments_b,  fig.height=4, fig.width=7, message=FALSE, warning=FALSE, paged.print=TRUE, fig.align="center"}
df_risky %>%
  mutate(label = paste0(billing_country_code, '-', shipping_country_code, str_replace(gateway, 'value_', '-'))) %>%
  ggplot(aes(x=cb_rate, y=approval_rate, size=total_approved_volume, color=label)) +
  geom_point(alpha=0.5) + 
  theme_ggcharts() +   
  labs(title = 'Chargeback vs. Approval Rate',
       subtitle = 'by Group',
       fill = '',
       size = 'Order Volume',
       x = 'Chargeback Rate',
       y = 'Approval Rate') + 
  theme(legend.position = 'right')
```

### Riskified Added Value
```{r riski_segments_c,  fig.height=4, fig.width=7, message=FALSE, warning=FALSE, paged.print=TRUE, fig.align="center"}

df_riski_kpis <- df %>% 
  group_by(across(required_features)) %>% 
  summarise(avg_riski_age = round(mean(V4_our_age), 1),
            avg_mer_age =round( mean(V5_merchant_age), 1),
            linking = round(sum(V1_link)/n(), 2))

df_added_value <- df_risky %>% 
  left_join(df_riski_kpis, by = required_features) %>%
  select(required_features, avg_riski_age, avg_mer_age, linking)

formattable(df_added_value, align =rep('c', 6))

```

--- 

## Sub-Optimal Performance {.tabset}

**Sub-Optimal Performance** will be defined as groups with the following attributes: 

  * Relatively **low Approval Rate**
* Relatively **low Chargeback Rate**

With the assumption of transaction that are mostly to be declined while having relatively low chargeback rate 
within specific groups, could be approved safely more then they current are.

### Table

```{r sop_segments_a,  fig.height=4, fig.width=7, message=FALSE, warning=FALSE, paged.print=TRUE, fig.align="center"}
df_sop <- df_aggregated  %>%
  filter(ar_z < -2, cbr_z < 0.25) %>%
  select(billing_country_code, shipping_country_code, gateway, total_orders,
         total_approved_volume, approval_rate, cb_rate) %>% 
  mutate_at(4:7, round, 3) %>%
  arrange(desc(total_approved_volume), desc(total_orders))

formattable(df_sop, align =rep('c', ncol(df_sop)), 
            list(
              `total_orders`= color_tile(customGreen0, customGreen),
              `total_approved_volume`= color_tile(customGreen0, customGreen),
              `approval_rate`= color_tile(customGreen0, customGreen),
              `cb_rate`= color_bar(customRed)
            ))
```

### Chart

```{r sop_segments_b,  fig.height=5.5, fig.width=7, message=FALSE, warning=FALSE, paged.print=TRUE, fig.align="center"}

df_sop %>%
  mutate(label = paste0(billing_country_code, '-', shipping_country_code, str_replace(gateway, 'value_', '-'))) %>%
  ggplot(aes(x=cb_rate, y=approval_rate, size=total_approved_volume, color=label)) +
  geom_point(alpha=0.5) + 
  theme_ggcharts() +   
  labs(title = 'Chargeback vs. Approval Rate',
       subtitle = 'by Group',
       fill = '',
       size = 'Order Volume',
       x = 'Chargeback Rate',
       y = 'Approval Rate') + 
  theme(legend.position = 'right')

```

### Riskified Added Value

```{r sop_segments_c,  fig.height=7, fig.width=7, message=FALSE, warning=FALSE, paged.print=TRUE, fig.align="center"}
df_added_value_sop <- df_sop %>% 
  left_join(df_riski_kpis, by = required_features) %>%
  select(required_features, avg_riski_age, avg_mer_age, linking)

formattable(df_added_value_sop, align =rep('c', ncol(df_added_value_sop)))
```

---


# Question II

### Fitting a Predictive Model

Executed by Python (base code under classifier.py)

```{python model_training, warning=FALSE}
from classifier import ModelExplained

try:
   # instance = ModelExplained(iteration_range=[500, 5000])
   # instance.main()
   print('Uncomment commands in order to trigger the model training proccess')
except Exception as e:
   print(e)
```

## Model Evaluation {.tabset}

### Threshold

```{r threshold,  fig.height=4, fig.width=7, message=FALSE, warning=FALSE, paged.print=TRUE, fig.align="center"}
df_th <- read.csv('data/plots/threshold.csv')

max_val <- df_th %>% 
  mutate(delta = approval_rate-90) %>% 
  summarise(ar = min(approval_rate[delta > 0]),
            th = min(threshold[approval_rate >= ar]),
            min_ar = min(approval_rate))

df_th %>% 
  ggplot(aes(x=approval_rate, y=threshold)) +
  geom_line()  + 
  theme_ggcharts() +   
  labs(title = 'Threshold vs. Approval Rate',
       subtitle = 'Goal: Fitting TH for getting 90% approval rate',
       y = 'Threshold',
       x = 'Approval Rate (%)',
       col = '') +
  geom_hline(yintercept = max_val$th, col='red') + 
  geom_text(aes(label=paste0(max_val$th),
                x = max_val$min_ar,
                y = max_val$th + 0.05,
                col = 'red')) + 
  theme(legend.position = 'none')
``` 

### Evaluation Metrics

#### Chossing Hyper Parameters

 * Number of Trees
* Learning Rate
* Depth

```{r hyper_params,  fig.height=4, fig.width=7, message=FALSE, warning=FALSE, paged.print=TRUE, fig.align="center"}
df_hyper_params <- read.csv('data/plots/hyper_params.csv')
df_prauc <- read.csv('data/plots/dataset_prauc.csv')

df_show <- df_hyper_params %>% arrange(desc(prauc)) %>%
  select(trees, learning_rate, depth, prauc, roc_auc) %>% head(10) %>%
  mutate_at(1:5, round, 2)

formattable(df_show, align =rep('c', ncol(df_show)),  lapply(1:nrow(df_show), function(row) {
  area(row= 1, col = 1:ncol(df_show)) ~ color_tile("lightpink", "lightpink")
}))

df_prauc %>%
  ggplot(aes(x=recall, y=precision)) +
  geom_line(size = 1, col = 'darkred') + 
  theme_ggcharts() +
  labs(title = 'Area Under Precision-Recall Curve',
       subtitle = 'PR AUC',
       x = 'Recall',
       y = 'Precision',
       color = '') +
  theme(legend.position = 'none',
        panel.border = element_rect(colour = "black", fill=NA, size=1))
  
``` 


### Business Interpretation

```{r business_inter , fig.height=4, fig.width=7, message=FALSE, warning=FALSE, paged.print=TRUE, fig.align="center"}

df_th <- read.csv('data/plots/threshold.csv')

threshold <- df_th %>% mutate(delta = approval_rate-90) %>% 
  summarise(ar = approval_rate[abs(delta) == min(abs(delta))],
            th = min(threshold[approval_rate >= ar])) %>%
  filter(ar >= 90)

df_test <- read.csv('data/plots/dataset_test.csv')

mutated_df_test <- df_test %>%
  mutate(model_declined = ifelse(model_score_1 >= threshold$th, T, F),
         model_status = case_when(
           model_declined ~ 'declined',
           (!model_declined) & status != 'chargeback' ~ 'approved',
           (!model_declined) & status == 'chargeback' ~ 'chargeback')) 

performence_kpi <- mutated_df_test %>% 
  summarise(
    order_count = n(),
    approval_rate_mer = sum(status != 'declined')/order_count,
    approval_rate_riski = sum(model_status != 'declined')/order_count,
    cb_count_mer = sum(status == 'chargeback'),
    cb_count_riski = sum(model_status == 'chargeback'),
    cb_paid_mer = sum(total_spent[status == 'chargeback']),
    cb_paid_riski = sum(total_spent[model_status == 'chargeback']),
    cb_rate_dollar_mer = cb_paid_mer/sum(total_spent[status != 'declined']),
    cb_rate_dollar_riski = cb_paid_riski/sum(total_spent[model_status != 'declined']),
    cb_rate_count_mer = cb_count_mer/sum(status != 'declined'),
    cb_rate_count_riski = cb_count_riski/sum(model_status != 'declined'),
    cb_saved_dollar = cb_paid_mer-cb_paid_riski,
    cb_saved_count = cb_count_mer-cb_count_riski,
    required_fee = 2*cb_paid_riski/sum(total_spent[model_status != 'declined'])
  )

output <- model_performence_comp(performence_kpi, 'mer') %>%
  left_join(model_performence_comp(performence_kpi, 'riski'), on = c('variable'))

cb_saved_pct <- paste0(round(performence_kpi$cb_saved_count*100/performence_kpi$cb_count_mer, 2), '%')
mutated_df_test <- mutated_df_test %>% filter(model_status == 'approved', status != 'declined') %>% count()

formattable(output, align =rep('c', 3))

```

### Insights

* We were able to save  **__`r cb_saved_pct`__** chargebacks.
* We approved **__`r mutated_df_test$n`__**  declines, those should be assessed.

---

# Question III

Based on the performance of the model I trained, the **fee** that we should quote the merchant 
in order **total cost of chargebacks to be 50% of our total revenue** will be calculated as follow:

* **volume**: Total volume of transactions that were approved (including chargebacks)
* **chargeback**: Chargeback paid by Riskified (according to the suggested model)
* **fee**: Required fee  

$$
\frac{1}{2} = \frac{chargeback}{volume*fee}
$$
$$
fee = \frac{2*chargeback}{volume}
$$

* Calculated result:

```{r merchant_fee , fig.height=4, fig.width=7, message=FALSE, warning=FALSE, paged.print=TRUE, fig.align="center"}
data <- tibble(`Required Fee` = paste0(round(performence_kpi$required_fee*100, 3),'%'))

formattable(data, align =rep('c', 1),  lapply(1:nrow(data), function(row) {
  area(row= 1, col = 1:1) ~ color_tile("lightblue", "lightblue")
}))
```

---

# Bonus Question

The probability that my model will score the approved order higher than the chargeback is the ROC AUC metric, as presented bellow.

```{r bonus , fig.height=4, fig.width=7, message=FALSE, warning=FALSE, paged.print=TRUE, fig.align="center"}
roc_auc <- (df_hyper_params %>% filter(prauc == max(prauc)) %>% head(1))$roc_auc
data_roc_auc <- tibble(`ROC AUC` = paste0(round(roc_auc*100, 3),'%'))

formattable(data_roc_auc, align =rep('c', 1),  lapply(1:nrow(data), function(row) {
  area(row= 1, col = 1:1) ~ color_tile("lightblue", "lightblue")
}))

# consider:
# data_approved <- mutated_df_test %>% filter(model_status != 'declined')
# val <- auc(data_approved$y, data_approved$model_score_1)




```

